On the performance of the MAC model

### 2018-10-30 2018_nips_vigil/mac.tex

The MAC network~\cite{hudsonManning18} is a recurrent model that performs reasoning 
using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
At the end, a suitable answer is given based on this composite reasoning.
To improve the accuracy of prediction, both the questions and images
are preprocessed suitably. For the question,  a word-embedding is first used to
transformed the question into a sequence of vectors which is then passed through
a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
corresponds to a unique word in the question and is called the 
\emph{contextual embedding} for that word.
Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.

\begin{wrapfigure}{r}[5pt]{0.4\textwidth}
	\vspace{-15pt}
	\centering
	\includegraphics[width=\textwidth]{img/mac_cell.pdf}
	\caption{The MAC cell~\cite{hudsonManning18}}
	\label{fig:mac_cell}
	\vspace{-5pt}
\end{wrapfigure}

>>>>

The MAC network~\cite{hudson2018compositional} is a recurrent model that performs reasoning 
using multiple steps, where each step involves sequentially analyzing a part of the question following which attention on the image is changed suitably.
At the end, a suitable answer is given based on this composite reasoning.
To improve the accuracy of prediction, both the questions and images
are preprocessed suitably. For the question,  a word-embedding is first used to
transformed the question into a sequence of vectors which is then passed through
a bidirectional LSTM to produce a sequence of hidden state pairs. Each such pair 
corresponds to a unique word in the question and is called the 
\emph{contextual embedding} for that word.
Similarly each image is initially processed using a pre-trained network (using ResNet) followed by two trainable CNN layers.

\begin{wrapfigure}{r}[5pt]{0.4\textwidth}
	\vspace{-15pt}
	\centering
	\includegraphics[width=\textwidth]{img/mac_cell.pdf}
	\caption{The MAC cell, reproduced on the basis of~\cite{hudson2018compositional}}
	\label{fig:mac_cell}
	\vspace{-5pt}
\end{wrapfigure}
